Urban Connectivity Dynamics: Analyzing Free Public WiFi Distribution in Toronto

### 2024-04-18 outputs/paper/paper.qmd
correct a typo
Delete unnecessary model

# IMPORT MODEL FROM OUTPUTS FOLDER
wifi_model <- readRDS(here::here("outputs/models/wifi_model.rds"))
population_model <- readRDS(here::here("outputs/models/population_model.rds"))
income_model <- readRDS(here::here("outputs/models/income_model.rds"))

@@

The findings of this study shed light on the intricate relationship between public WiFi distribution and urban social characteristics in Toronto. The intricate dynamics surrounding public WiFi distribution in Toronto encompass a multitude of factors that interact to shape urban wareless Internet connectivity.      Beyond simplistic correlations, this study delves into the interplay between the distribution of public wifi, income, population, and building types.

@@

# Appendix

For enhancement, I take advantage of shiny, which is to quickly add some interactivity to our graphs according to the simulated data. Here(@fig-shiny) is the screnshot of my shiny work, and the interactive graphis is in the folder "Enhancement - Shiny Plot".

>>>>

# IMPORT MODEL FROM OUTPUTS FOLDER
population_model <- readRDS(here::here("outputs/models/population_model.rds"))
income_model <- readRDS(here::here("outputs/models/income_model.rds"))

@@

The findings of this study shed light on the intricate relationship between public Wifi distribution and urban social characteristics in Toronto. The intricate dynamics surrounding public WiFi distribution in Toronto encompass a multitude of factors that interact to shape urban wareless Internet connectivity. Beyond simplistic correlations, this study delves into the interplay between the distribution of public wifi, income, population, and building types.

@@

\newpage
# Appendix

For enhancement, I take advantage of shiny, which is to quickly add some interactivity to our graphs according to the simulated data. Here(@fig-shiny) is the screnshot of my shiny work, and the interactive graph is is in the folder "Enhancement - Shiny Plot".
